Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-17 doc/Response.Rmd

Overall, this paper presents a nice incremental improvement to a promising algorithmic approach. A number of major revisions are required prior to acceptance as described above. Note that these revisions all relate to the writing and require no additional experiments to be performed. They improve the clarity and preciseness of the manuscript and serve to address questions that readers will have.

## Reviewer #2

You may not fully appreciate and how critical their phase orientations used to identify fired bullets (LEAs).  This important consideration should have been an important  aspect of the experiment and not instead focus primarily only LEA comparisons.  While each area is in practice independently compared microscopically or by surface profile algorithms, consideration as to their orientation in their position in the barrel rifling, and correlations of LEAs cannot ignore the phase of positions.  Including the phase consideration of the fired bullet comparisons, the success of finding a match in a particular position between two bullets is significantly increased and demonstrated in their reference Chu, et al.  If you are to base independent single LEA scoring to test the method, you should make this clearer in the beginning of your paper and hypothesis, and not discuss it finally in the last sentence of the document body.
If you are going to compare method performance between chisel/tool stria to LEAs on bullets, you should have a detailed discussion as to the large differences in the toolmark widths that are in consideration.  The Chumbley scoring parameters may have been optimized for chisel widths but may not be optimal for the LEAs.

*Thank you for your comments, we appreciate your insight. You are right, for the purpose of matching bullet to bullet, all lands of each of the bullets and their relative positions on the bullet should be considered. This is not the problem we tried to address in this manuscript. To get from land-to-land comparisons to bullet-to-bullet comparisons, an additional step is required. In \cite{chu2010}, the average correlation value is taken. In this manuscript, the land-to-land comparisons result in a p-value. There are different options to aggregate these values at this stage to quantify a bullet-bullet comparison.
*

*We agree on the point that the toolmarks have large differences in width and the parameters of the chumbley algorithm are optimized for tools, which is why we first do a parameter study to identify the best set of parameters that would work for the LEAs.*

### 2018-08-17 doc/paper.Rmd
Update paper.Rmd

\gk{changed} These digitized markings allow the use of statistical methods which can quantify the scientific mechanism of comparing markings and serve as basis for an error rate calculation.
In \cite{manytoolmarks2} a relative distance metric is defined and used as similarity measure between two toolmarks. This approach is expanded in \citet{manytoolmarks1}: a set of small segments in the markings of two toolmarks are extracted and  similarity is compared using a maximum Pearson correlation coefficient. 
The Chumbley scoring method, first introduced in \cite{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  In \cite{hadler}  the score is fixed to be deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segments of striae.

>>>>

\gk{changed} These digitized markings allow the use of statistical methods to quantify the scientific mechanism of comparing markings and serve as basis for an error rate calculation.
In \cite{manytoolmarks2} a relative distance metric is defined and used as similarity measure between two toolmarks. This approach is expanded in \citet{manytoolmarks1}: a set of small segments in the markings of two toolmarks are extracted and  similarity is compared using a maximum Pearson correlation coefficient. 
The Chumbley scoring method, first introduced in \cite{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  In \cite{hadler}  the score is fixed to be deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segments of striae.
